---
title: "Assignment 2"
author: 
  - name: "Misati Nyambane"
    id: "670145"
  - name: "Nathan Orang'o"
    id: "670637"
  - name: "Sylvia Njane"
    id: "669203"
  - name: "Sharlyne Kiven"
    id: "ID004"
  - name: "Rita Magu"
    id: "6668940"
  - name: "Abdullahi Sundus"
    id: "ID006"
  - name: "Kimani Jessica"
    id: "ID006" 
output: pdf_document
date: "`r format(Sys.Date(), '%B %d, %Y')`"
---

## Libraries

The following libraries will be needed in order to work with the data. The importance of each library is as detailed below:

-   `dplyr`: The manipulate the data set.
-   `fitdistrplus`: To fit different distributions to the data set.
-   `readxl`: To read the `.xlsx` file that the data is in
-   `lubridate`: To handle date operations and manipulations.
-   `naniar`: To check if any values are missing displaying a visual representation of the location where there are missing values.
-   `ggplot2`:
-   `plotly`:

```{r}
library(dplyr)
library(fitdistrplus)
library(readxl)
library(lubridate)
library(naniar)
library(ggplot2)
library(plotly)
```

## Part a

### Data Normalization

Firstly, the data is imported using the `read_excel` function. Then a quick snapshot using `head` is done.

```{r}
patient_data <- read_excel("~/Library/CloudStorage/Dropbox/My Mac (Nathans-MacBook-Air.local)/Downloads/Final Patient Data Group Work (1).xlsx")

head(patient_data)
```

Soon after `vis_miss` is employed to visually pinpoint the points in the data frame where data is missing.

```{r}
vis_miss(patient_data)
```

## Part b

A function for fitting distributions is created alongside a list of distributions that will be used. This eliminates redundancy and makes the code modular.

```{r}
fit_distributions <- function(column, distributions, subset_name) {
  
  for (dist in distributions) {
    if (dist == "beta") {
      # Ensure data is within [0, 1] for beta distribution
      if (all(column >= 0 & column <= 1)) {
        fit_result <- try(fitdist(column, dist), silent = TRUE)
      } else {
        # Apply min-max normalization if data is not in [0, 1]
        normalized_column <- (column - min(column)) / (max(column) - min(column))
        fit_result <- try(fitdist(normalized_column, dist), silent = TRUE)
      }
    } else {
      # Fit other distributions as usual
      fit_result <- try(fitdist(column, dist), silent = TRUE)
    }
    
    # Dynamically create variable name: e.g., fit_male_patients_beta
    variable_name <- paste0("fit_", subset_name, "_", dist)
    
    # Assign the fit result to the dynamically created variable
    assign(variable_name, fit_result, envir = .GlobalEnv)
  }
}

distributions_to_check <- c("norm", "lnorm", "gamma", "weibull", "exp", 
                            "cauchy", "logis", "unif")
```

Moreover, a function to find the model with the best AIC and BIC is as follows:

```{r}
find_best_aic_bic <- function(fits_list) {

  best_aic_model <- NULL
  best_bic_model <- NULL
  min_aic <- Inf
  min_bic <- Inf

  for (name in names(fits_list)) {
    fit <- fits_list[[name]]
    
    # Calculate AIC and BIC
    current_aic <- AIC(fit)
    current_bic <- BIC(fit)

    if (current_aic < min_aic) {
      min_aic <- current_aic
      best_aic_model <- name
    }

    if (current_bic < min_bic) {
      min_bic <- current_bic
      best_bic_model <- name
    }
  }
  
  # Return a list containing the results
  return(list(
    best_aic_model = best_aic_model,
    best_bic_model = best_bic_model,
    min_aic = min_aic,
    min_bic = min_bic
  ))
}
```

```{r}
get_negative_rows <- function(data, column_names = NULL) {
  # If column names are provided, check only those columns
  if (!is.null(column_names)) {
    negative_rows <- data %>%
      filter(if_any(all_of(column_names), ~ . < 0))  # Check for negative values in specified columns
  } else {
    # If no columns are specified, check all numeric columns
    negative_rows <- data %>%
      filter(if_any(where(is.numeric), ~ . < 0))  # Check for negative values in all numeric columns
  }
  
  return(negative_rows)
}
```

### Data Imputation

For each column a different method of handling missing values is employed:

1.  For the sex of the patient *mode imputation* is used where the most common value is used to replace any missing values for the sex of the patient.

```{r}
mode_impute <- function(x) {
  uniq <- unique(x)
  uniq[which.max(tabulate(match(x, uniq)))]
}

patient_data <- patient_data %>%
  mutate(Sex_Patient = if_else(is.na(Sex_Patient), mode_impute(Sex_Patient), Sex_Patient))
```

2.  For the Age of the patient *median imputation* is used where the middle value of all the ages is used to replace any missing values.

```{r}
patient_data <- patient_data %>%
  mutate(Age = if_else(is.na(Age), median(Age, na.rm = TRUE), Age))
```

3.  For the date someone checked in and checked out at the hospital *mode imputation* is used where the most common value for each is used to replace missing values in each column respectively. The validity of the date is also checked and if the date someone checked in is after the date they checked out then the date was inputted incorrectly and the values are swapped.

```{r}
patient_data <- patient_data %>%
  mutate(Date_Started = if_else(is.na(Date_Started), mode_impute(Date_Started), Date_Started))
```

```{r}
patient_data <- patient_data %>%
  mutate(Date_Ended = if_else(is.na(Date_Ended), mode_impute(Date_Ended), Date_Ended))
```

```{r}
patient_data <- patient_data %>%
  mutate(
    Date_Started = if_else(grepl("^\\d{2}-\\d{2}-\\d{3}$", Date_Started) | is.na(Date_Started), mode_impute(Date_Started), Date_Started),
    Date_Ended = if_else(grepl("^\\d{2}-\\d{2}-\\d{3}$", Date_Ended) | is.na(Date_Ended), mode_impute(Date_Ended), Date_Ended)
  )
```

```{r}
patient_data <- patient_data %>%
  mutate(
    Date_Started = as.Date(Date_Started, format = "%d-%m-%Y"),
    Date_Ended = as.Date(Date_Ended, format = "%d-%m-%Y")
  )

patient_data <- patient_data %>%
  mutate(
    temp = Date_Started,
    Date_Started = if_else(Date_Started > Date_Ended, Date_Ended, Date_Started),
    Date_Ended = if_else(temp > Date_Ended, temp, Date_Ended)
  ) %>%
  mutate(temp = NULL)
```

### Data Computation

The number of days is then computed from the date someone checked in and the date they checked out.

```{r}
patient_data <- patient_data %>%
  mutate(
    Days = as.numeric(Date_Ended - Date_Started),  # Calculate the difference in days
    
    # If Days is negative, recalculate using Date_Started - Date_Ended
    Days = if_else(Days < 0, as.numeric(Date_Started - Date_Ended), Days)
  )
```

### Data Validation

It is confirmed that all the days are greater than zero and that there are no missing values in the entire data set.

```{r}
vis_miss(patient_data)
```

```{r}
get_negative_rows(patient_data, column_names = c("Days"))
```

## Part c

### Data Splitting

The various different data sets needed are subsetted.

```{r}
male_patients <- patient_data %>%
  filter(Sex_Patient == "Male")

female_patients <- patient_data %>%
  filter(Sex_Patient == "Female")

non_resident_patients <- patient_data %>%
  filter(Facility_Type == "Non Resident")

resident_patients <- patient_data %>%
  filter(Facility_Type == "Resident")
```

### Data Analysis

The distributions are fitted for each data set.

```{r warning=FALSE}
data_sets <- list(
  all_patients = patient_data,
  male_patients = male_patients,
  female_patients = female_patients,
  non_resident_patients = non_resident_patients,
  resident_patients = resident_patients
)

for (data_name in names(data_sets)) {
  data_subset <- data_sets[[data_name]]

  column_to_fit <- data_subset$Days

  fit_distributions(column_to_fit, distributions_to_check, data_name)
}
```

```{r}
fit_variables <- ls(pattern = "^fit_")

fit_variables
```

```{r}
for (var in fit_variables) {
  cat("Summary of", var, ":\n")
  fit_result <- try(get(var), silent = TRUE)
  
  if (inherits(fit_result, "try-error")) {
    cat("Error in retrieving", var, ": Object not found or is a function.\n\n")
  } else if (is.function(fit_result)) {
    cat("Error: Object", var, "is a function, not a fit result.\n\n")
  } else {
    print(summary(fit_result))
  }
  
  cat("\n")  # Add a newline for readability between summaries
}
```

#### All Patients

Finally, we confirm our visual decision using the BIC and AIC of the models.

```{r}
fits_all_patients_list <- list(
  cauchy = fit_all_patients_cauchy,
  exp = fit_all_patients_exp,
  gamma = fit_all_patients_gamma,
  lnorm = fit_all_patients_lnorm,
  logis = fit_all_patients_logis,
  norm = fit_all_patients_norm,
  unif = fit_all_patients_unif,
  weibull = fit_all_patients_weibull
)

best_all_patients_models <- find_best_aic_bic(fits_all_patients_list)

cat("Best model by AIC:", best_all_patients_models$best_aic_model, "with AIC =", best_all_patients_models$min_aic, "\n")
cat("Best model by BIC:", best_all_patients_models$best_bic_model, "with BIC =", best_all_patients_models$min_bic, "\n")
```

#### Male Patients

```{r}
actual_plot <- ggplot(male_patients, aes(x = Days)) +
  geom_histogram(aes(y = after_stat(density)), bins = 10, fill = '#8F17FF', alpha = 0.5, color = "black") +
  geom_density(color = '#1736FF', linewidth = 1.5) +
  labs(title = 'Actual Ogive', x = "Number of Days at Hospital",y='Density')
actual_plot
```

```{r}
cauchy_loc_m <- fit_male_patients_cauchy$estimate["location"]
cauchy_scale_m <- fit_male_patients_cauchy$estimate["scale"]

exp_rate_m <- fit_male_patients_exp$estimate["rate"]

gamma_shape_m <- fit_male_patients_gamma$estimate["shape"]
gamma_rate_m <- fit_male_patients_gamma$estimate["rate"]

lognorm_meanlog_m <- fit_male_patients_lnorm$estimate["meanlog"]
lognorm_sdlog_m <- fit_male_patients_lnorm$estimate["sdlog"]

logis_location_m <- fit_male_patients_logis$estimate["location"]
logis_scale_m <- fit_male_patients_logis$estimate["scale"]

norm_mean_m <- fit_male_patients_norm$estimate["mean"]
norm_sd_m <- fit_male_patients_norm$estimate["sd"]

weibull_shape_m <- fit_male_patients_weibull$estimate["shape"]
weibull_scale_m <- fit_male_patients_weibull$estimate["scale"]

x_males <- seq(min(male_patients$Days), max(male_patients$Days), length.out = 100)

# Calculate density values for each distribution over the new x_males range
cauchy_density <- dcauchy(x_males, location = fit_male_patients_cauchy$estimate[1], scale = fit_male_patients_cauchy$estimate[2])
exp_density <- dexp(x_males, rate = fit_male_patients_exp$estimate[1])
gamma_density <- dgamma(x_males, shape = fit_male_patients_gamma$estimate[1], rate = fit_male_patients_gamma$estimate[2])
lognorm_density <- dlnorm(x_males, meanlog = fit_male_patients_lnorm$estimate[1], sdlog = fit_male_patients_lnorm$estimate[2])
logis_density <- dlogis(x_males, location = fit_male_patients_logis$estimate[1], scale = fit_male_patients_logis$estimate[2])
norm_density <- dnorm(x_males, mean = fit_male_patients_norm$estimate[1], sd = fit_male_patients_norm$estimate[2])
unif_density <- dunif(x_males, min = fit_male_patients_unif$estimate[1], max = fit_male_patients_unif$estimate[2])
weibull_density <- dweibull(x_males, shape = fit_male_patients_weibull$estimate[1], scale = fit_male_patients_weibull$estimate[2])

# Create histogram
fig_m <- plot_ly(male_patients, x = ~Days, type = 'histogram', 
                  histnorm = 'density', binwidth = 75, 
                  marker = list(color = 'blue', opacity = 0.6), name = 'Histogram')

# Add smooth density curve
fig_m <- fig_m %>% add_trace(x = density(male_patients$Days)$x, 
                              y = density(male_patients$Days)$y, 
                              type = 'scatter', mode = 'lines', 
                              line = list(color = 'black', width = 1.5), 
                              name = 'Density')

# Add distribution curves
fig_m <- fig_m %>% add_trace(x = x_males, y = cauchy_density, 
                              type = 'scatter', mode = 'lines', 
                              line = list(color = 'purple', width = 1.2), 
                              name = 'Cauchy')

fig_m <- fig_m %>% add_trace(x = x_males, y = exp_density, 
                              type = 'scatter', mode = 'lines', 
                              line = list(color = 'green', width = 1.2), 
                              name = 'Exponential')

fig_m <- fig_m %>% add_trace(x = x_males, y = gamma_density, 
                              type = 'scatter', mode = 'lines', 
                              line = list(color = 'orange', width = 1.2), 
                              name = 'Gamma')

fig_m <- fig_m %>% add_trace(x = x_males, y = lognorm_density, 
                              type = 'scatter', mode = 'lines', 
                              line = list(color = 'brown', width = 1.2), 
                              name = 'Log-normal')

fig_m <- fig_m %>% add_trace(x = x_males, y = logis_density,
                         type = 'scatter', mode = 'lines',
                         line = list(color = 'cyan', width = 1.2),
                         name = 'Logistic')

fig_m <- fig_m %>% add_trace(x = x_males, y = norm_density,
                         type = 'scatter', mode = 'lines',
                         line = list(color = 'red', width = 1.2),
                         name = 'Normal')

fig_m <- fig_m %>% add_trace(x = x_males, y = unif_density,
                         type = 'scatter', mode = 'lines',
                         line = list(color = 'pink', width = 1.2),
                         name = 'Uniform')

fig_m <- fig_m %>% add_trace(x = x_males, y = weibull_density,
                         type = 'scatter', mode = 'lines',
                         line = list(color = 'magenta', width = 1.2),
                         name = 'Weibull')

# Layout settings: titles, axis labels, and legend
fig_m <- fig_m %>% layout(title = 'Histogram with Fitted Distributions for Male Patients',
                      xaxis = list(title = 'Number of Days at Hospital',
                                   range = c(0, NA),  # Ensure x-axis starts at 0
                                   zeroline = TRUE),   # Ensure zero line is present
                      yaxis = list(title = 'Density'),
                      legend = list(title = list(text = 'Distributions')),
                      barmode = 'overlay')

fig_m
```

Finally, we confirm our visual decision using the BIC and AIC of the models.

```{r}
fits_male_patients_list <- list(
  cauchy = fit_male_patients_cauchy,
  exp = fit_male_patients_exp,
  gamma = fit_male_patients_gamma,
  lnorm = fit_male_patients_lnorm,
  logis = fit_male_patients_logis,
  norm = fit_male_patients_norm,
  unif = fit_male_patients_unif,
  weibull = fit_male_patients_weibull
)

best_male_patients_models <- find_best_aic_bic(fits_male_patients_list)

cat("Best model by AIC:", best_male_patients_models$best_aic_model, "with AIC =", best_male_patients_models$min_aic, "\n")
cat("Best model by BIC:", best_male_patients_models$best_bic_model, "with BIC =", best_male_patients_models$min_bic, "\n")
```

#### Female Patients

Finally, we confirm our visual decision using the BIC and AIC of the models.

```{r}
fits_female_patients_list <- list(
  cauchy = fit_female_patients_cauchy,
  exp = fit_female_patients_exp,
  gamma = fit_female_patients_gamma,
  lnorm = fit_female_patients_lnorm,
  logis = fit_female_patients_logis,
  norm = fit_female_patients_norm,
  unif = fit_female_patients_unif,
  weibull = fit_female_patients_weibull
)

best_female_patients_models <- find_best_aic_bic(fits_female_patients_list)

cat("Best model by AIC:", best_female_patients_models$best_aic_model, "with AIC =", best_female_patients_models$min_aic, "\n")
cat("Best model by BIC:", best_female_patients_models$best_bic_model, "with BIC =", best_female_patients_models$min_bic, "\n")
```

#### Resident Patients
#### Plotting the Histogram and Fitting Distributions

```{r}
# Filtering the data to get only the "Resident" patients
resident_patients <- patient_data %>%
  filter(Facility_Type == "Resident")

# Extracting the number of days for Resident patients
days_residents <- resident_patients$Days

# Generating a sequence of x values for plotting density curves
x_residents <- seq(min(days_residents), max(days_residents), length.out = 100)

# Calculating densities for each distribution over the x_residents range
# Extracting parameters from fitted distributions for the Resident patients

cauchy_density <- dcauchy(x_residents, location = fit_resident_patients_cauchy$estimate[1], scale = fit_resident_patients_cauchy$estimate[2])
exp_density <- dexp(x_residents, rate = fit_resident_patients_exp$estimate[1])
gamma_density <- dgamma(x_residents, shape = fit_resident_patients_gamma$estimate[1], rate = fit_resident_patients_gamma$estimate[2])
lognorm_density <- dlnorm(x_residents, meanlog = fit_resident_patients_lnorm$estimate[1], sdlog = fit_resident_patients_lnorm$estimate[2])
logis_density <- dlogis(x_residents, location = fit_resident_patients_logis$estimate[1], scale = fit_resident_patients_logis$estimate[2])
norm_density <- dnorm(x_residents, mean = fit_resident_patients_norm$estimate[1], sd = fit_resident_patients_norm$estimate[2])
unif_density <- dunif(x_residents, min = min(days_residents), max = max(days_residents))
weibull_density <- dweibull(x_residents, shape = fit_resident_patients_weibull$estimate[1], scale = fit_resident_patients_weibull$estimate[2])

# Creating an interactive histogram using plotly
fig_r <- plot_ly(resident_patients, x = ~Days, type = 'histogram', 
                 histnorm = 'density', binwidth = 75, 
                 marker = list(color = 'blue', opacity = 0.6), name = 'Histogram')

# Adding a smooth density curve
fig_r <- fig_r %>% add_trace(x = density(days_residents)$x, 
                             y = density(days_residents)$y, 
                             type = 'scatter', mode = 'lines', 
                             line = list(color = 'black', width = 1.5), 
                             name = 'Density')

# Adding Cauchy distribution curve
fig_r <- fig_r %>% add_trace(x = x_residents, y = cauchy_density, 
                             type = 'scatter', mode = 'lines', 
                             line = list(color = 'purple', width = 1.2), 
                             name = 'Cauchy')

# Adding Exponential distribution curve
fig_r <- fig_r %>% add_trace(x = x_residents, y = exp_density, 
                             type = 'scatter', mode = 'lines', 
                             line = list(color = 'green', width = 1.2), 
                             name = 'Exponential')

# Adding Gamma distribution curve
fig_r <- fig_r %>% add_trace(x = x_residents, y = gamma_density, 
                             type = 'scatter', mode = 'lines', 
                             line = list(color = 'orange', width = 1.2), 
                             name = 'Gamma')

# Adding Log-normal distribution curve
fig_r <- fig_r %>% add_trace(x = x_residents, y = lognorm_density, 
                             type = 'scatter', mode = 'lines', 
                             line = list(color = 'brown', width = 1.2), 
                             name = 'Log-normal')

# Adding Logistic distribution curve
fig_r <- fig_r %>% add_trace(x = x_residents, y = logis_density, 
                             type = 'scatter', mode = 'lines', 
                             line = list(color = 'cyan', width = 1.2), 
                             name = 'Logistic')

# Adding Normal distribution curve
fig_r <- fig_r %>% add_trace(x = x_residents, y = norm_density, 
                             type = 'scatter', mode = 'lines', 
                             line = list(color = 'red', width = 1.2), 
                             name = 'Normal')

# Adding Uniform distribution curve
fig_r <- fig_r %>% add_trace(x = x_residents, y = unif_density, 
                             type = 'scatter', mode = 'lines', 
                             line = list(color = 'pink', width = 1.2), 
                             name = 'Uniform')

# Adding Weibull distribution curve
fig_r <- fig_r %>% add_trace(x = x_residents, y = weibull_density, 
                             type = 'scatter', mode = 'lines', 
                             line = list(color = 'magenta', width = 1.2), 
                             name = 'Weibull')

# Outlining Plot Layout settings: titles, axis labels, and legend
fig_r <- fig_r %>% layout(title = 'Histogram with Fitted Distributions for Resident Patients',
                          xaxis = list(title = 'Number of Days at Hospital', 
                                       range = c(0, NA),  # Ensure x-axis starts at 0
                                       zeroline = TRUE),   # Ensure zero line is present
                          yaxis = list(title = 'Density'),
                          legend = list(title = list(text = 'Distributions')),
                          barmode = 'overlay')

# Displaying the plot
fig_r



```

Finally, we confirm our visual decision using the BIC and AIC of the models.

```{r}
fits_resident_patients_list <- list(
  cauchy = fit_resident_patients_cauchy,
  exp = fit_resident_patients_exp,
  gamma = fit_resident_patients_gamma,
  lnorm = fit_resident_patients_lnorm,
  logis = fit_resident_patients_logis,
  norm = fit_resident_patients_norm,
  unif = fit_resident_patients_unif,
  weibull = fit_resident_patients_weibull
)

best_resident_patients_models <- find_best_aic_bic(fits_resident_patients_list)

cat("Best model by AIC:", best_resident_patients_models$best_aic_model, "with AIC =", best_resident_patients_models$min_aic, "\n")
cat("Best model by BIC:", best_resident_patients_models$best_bic_model, "with BIC =", best_resident_patients_models$min_bic, "\n")
```
#### Explanation for the selected best-fit distribution
From the BIC, the best fitting `residents` distribution is `Exponential Distribution`. This indicates that most `Resident patients` have a relatively short stay, with the likelihood of a longer stay decreasing exponentially. 

This may point to a situation where most patients recover and are discharged quickly, and the few cases that extend their stay may be due to complications or more complex care requirements. 

#### Possible Insights
1. As most patient stays are short, the hospital should allocate sufficient resources for initial patient assessments and treatment (Improved Triage)
2. Focus on high quality intensive care to prevent complications that may further patient stay. 
3. Identifying common causes of extended patient stay and addressing them appropriately


#### Non-resident Patients

```{r warning=FALSE}
ggplot(non_resident_patients, aes(x = Days)) +
  geom_histogram(binwidth = 75, fill = "blue", color = "red") +
  labs(title = 'Histogram Distribution of Days for Non Residents', 
       x = 'Number of Days at Hospital', 
       y = 'Number of Non Residents') +
  xlim(0, NA)

```

```{r}
# Extract parameters from fitted distributions
cauchy_loc <- fit_non_resident_patients_cauchy$estimate["location"]
cauchy_scale <- fit_non_resident_patients_cauchy$estimate["scale"]

exp_rate <- fit_non_resident_patients_exp$estimate["rate"]

gamma_shape <- fit_non_resident_patients_gamma$estimate["shape"]
gamma_rate <- fit_non_resident_patients_gamma$estimate["rate"]

lognorm_meanlog <- fit_non_resident_patients_lnorm$estimate["meanlog"]
lognorm_sdlog <- fit_non_resident_patients_lnorm$estimate["sdlog"]

logis_location <- fit_non_resident_patients_logis$estimate["location"]
logis_scale <- fit_non_resident_patients_logis$estimate["scale"]

norm_mean <- fit_non_resident_patients_norm$estimate["mean"]
norm_sd <- fit_non_resident_patients_norm$estimate["sd"]

weibull_shape <- fit_non_resident_patients_weibull$estimate["shape"]
weibull_scale <- fit_non_resident_patients_weibull$estimate["scale"]

# Generate x values for the density curves
x_vals <- seq(min(non_resident_patients$Days), max(non_resident_patients$Days), length.out = 100)

# Compute densities for each distribution
cauchy_density <- dcauchy(x_vals, location = cauchy_loc, scale = cauchy_scale)
exp_density <- dexp(x_vals, rate = exp_rate)
gamma_density <- dgamma(x_vals, shape = gamma_shape, rate = gamma_rate)
lognorm_density <- dlnorm(x_vals, meanlog = lognorm_meanlog, sdlog = lognorm_sdlog)
logis_density <- dlogis(x_vals, location = logis_location, scale = logis_scale)
norm_density <- dnorm(x_vals, mean = norm_mean, sd = norm_sd)
unif_density <- dunif(x_vals, min = min(non_resident_patients$Days), max = max(non_resident_patients$Days))
weibull_density <- dweibull(x_vals, shape = weibull_shape, scale = weibull_scale)

# Create histogram
fig_nr <- plot_ly(non_resident_patients, x = ~Days, type = 'histogram', 
               histnorm = 'density', binwidth = 75, 
               marker = list(color = 'blue', opacity = 0.6), name = 'Histogram')

# Add smooth density curve
fig_nr <- fig_nr %>% add_trace(x = density(non_resident_patients$Days)$x, 
                         y = density(non_resident_patients$Days)$y, 
                         type = 'scatter', mode = 'lines', 
                         line = list(color = '#1736FF', width = 1.5), 
                         name = 'Density')

# Add Cauchy distribution curve
fig_nr <- fig_nr %>% add_trace(x = x_vals, y = cauchy_density, 
                         type = 'scatter', mode = 'lines', 
                         line = list(color = 'purple', width = 1.2), 
                         name = 'Cauchy')

# Add Exponential distribution curve
fig_nr <- fig_nr %>% add_trace(x = x_vals, y = exp_density, 
                         type = 'scatter', mode = 'lines', 
                         line = list(color = 'green', width = 1.2), 
                         name = 'Exponential')

# Add Gamma distribution curve
fig_nr <- fig_nr %>% add_trace(x = x_vals, y = gamma_density, 
                         type = 'scatter', mode = 'lines', 
                         line = list(color = 'orange', width = 1.2), 
                         name = 'Gamma')

# Add Log-normal distribution curve
fig_nr <- fig_nr %>% add_trace(x = x_vals, y = lognorm_density, 
                         type = 'scatter', mode = 'lines', 
                         line = list(color = 'brown', width = 1.2), 
                         name = 'Log-normal')

# Add Logistic distribution curve
fig_nr <- fig_nr %>% add_trace(x = x_vals, y = logis_density, 
                         type = 'scatter', mode = 'lines', 
                         line = list(color = 'cyan', width = 1.2), 
                         name = 'Logistic')

# Add Normal distribution curve
fig_nr <- fig_nr %>% add_trace(x = x_vals, y = norm_density, 
                         type = 'scatter', mode = 'lines', 
                         line = list(color = 'red', width = 1.2), 
                         name = 'Normal')

# Add Uniform distribution curve
fig_nr <- fig_nr %>% add_trace(x = x_vals, y = unif_density, 
                         type = 'scatter', mode = 'lines', 
                         line = list(color = 'pink', width = 1.2), 
                         name = 'Uniform')

# Add Weibull distribution curve
fig_nr <- fig_nr %>% add_trace(x = x_vals, y = weibull_density, 
                         type = 'scatter', mode = 'lines', 
                         line = list(color = 'magenta', width = 1.2), 
                         name = 'Weibull')

# Layout settings: titles, axis labels, and legend
fig_nr <- fig_nr %>% layout(title = 'Histogram with Fitted Distributions for Non-Residents',
                      xaxis = list(title = 'Number of Days at Hospital', 
                                   range = c(0, NA),  # Ensure x-axis starts at 0
                                   zeroline = TRUE),   # Ensure zero line is present
                      yaxis = list(title = 'Density'),
                      legend = list(title = list(text = 'Distributions')),
                      barmode = 'overlay')

# Show the plot
fig_nr
```

Finally, we confirm our visual decision using the BIC and AIC of the models.

```{r}
fits_non_resident_patients_list <- list(
  cauchy = fit_non_resident_patients_cauchy,
  exp = fit_non_resident_patients_exp,
  gamma = fit_non_resident_patients_gamma,
  lnorm = fit_non_resident_patients_lnorm,
  logis = fit_non_resident_patients_logis,
  norm = fit_non_resident_patients_norm,
  unif = fit_non_resident_patients_unif,
  weibull = fit_non_resident_patients_weibull
)

best_non_resident_patients_models <- find_best_aic_bic(fits_non_resident_patients_list)

cat("Best model by AIC:", best_non_resident_patients_models$best_aic_model, "with AIC =", best_non_resident_patients_models$min_aic, "\n")
cat("Best model by BIC:", best_non_resident_patients_models$best_bic_model, "with BIC =", best_non_resident_patients_models$min_bic, "\n")
```

## Part d

### Data Distribution Identification

## Part e

### Data Stories
